### 2019-06-13 initial/notes.tex
okok understand what's going on now

Though this section is located before the weak tidal friction section, we
actually return to this second toy problem to get some practice on the Henrard
paper, to confirm the accuracy of our simulations compared to analytical
predictions, and to get some practice doing these new integrals. Consider the
dissipation-free Cassini state system with a small but constant $\pd{\eta}{t} =
\epsilon$. For clarity, the Hamiltonian is
\begin{equation}
    H = -\frac{\mu^2}{2} + \eta
        \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2} \theta \cos \phi}.
\end{equation}

For an arbitrary initial condition outside of the separatrix, we want: (i) to
know when it will encounter the separatrix, and (ii) what its fate will be. We
will begin with (ii) since it is the more fun problem. We know that this boils
down to the Melnikov-like formula
\begin{equation}
    B_i = \int_{\mathcal{C}_i} \dot{\eta}\pd{\Delta H}{\eta}
        \;\mathrm{d}t.
\end{equation}
$B_i$ is the change in $\Delta H = H_4 - H$ over contour $\mathcal{C}_i$.

@@

\subsection{Weak Perturber Hopping Revisited}

>>>>

Though this section is located before the weak tidal friction section, we
actually return to this second toy problem to get some practice on the Henrard
paper, to confirm the accuracy of our simulations compared to analytical
predictions, and to get some practice doing these new integrals. Consider the
dissipation-free Cassini state system with a small but constant $\pd{\eta}{t} =
\epsilon$. For clarity, the Hamiltonian is
\begin{equation}
    H = -\alpha\frac{\mu^2}{2} +
        \mu \cos I - \sin I \sqrt{1 - \mu^2} \theta \cos \phi.
\end{equation}
This proves to be the algebraically easiest formulation, instead of using
$\eta$.

For an arbitrary initial condition outside of the separatrix, we want: (i) to
know when it will encounter the separatrix, and (ii) what its fate will be. We
will begin with (ii) since it is the more fun problem. We know that this boils
down to the Melnikov-like formula
\begin{equation}
    B_i = \int_{\mathcal{C}_i} \dot{\alpha}\pd{\Delta H}{\alpha}
        \;\mathrm{d}t.
\end{equation}
$B_i$ is the change in $\Delta H = H_4 - H$ over contour $\mathcal{C}_i$.

In order to probe the relevant physics here, we firsst cite without proof (refer
to \autoref{ss:revisited} for this) that $\pd{\Delta H}{\alpha} =
\frac{\mu^2}{2} - \frac{1}{2\alpha^2}\cos^2 I$. This implies that
\begin{equation}
    B_i = \int_{\mathcal{C}_i} \dot{\alpha}\s*{
        \frac{\mu^2}{2} - \frac{1}{2\alpha^2}\cos^2 I}
        \;\mathrm{d}t.
\end{equation}
Recall that the capture probability is $\frac{B_1 + B_2}{B_1}$ when this
expression is $\in [0, 1]$. However, we immediately see a problem: the first
term will dominate the second term, since $\alpha \gg 1$, but the first term is
also positive semidefinite. This implies $B_1, B_2$ will always have the same
sign unless $\dot{\alpha}$ has different signs over the two trajectories!

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$.

@@

\subsection{Weak Perturber Hopping Revisited}\label{ss:revisited}
